\section{Introduction}
% no \IEEEPARstart
We describe five challenge problems at the foundations of Cyber-Physical Systems (CPS). CPS are the new generation of time-critical and safety-critical Real-Time Embedded Systems where computation and communication are tightly coupled to control large, complex and ``messy" plants. Unlike classical Real-Time Systems where the system is designed in a constrained manner to limit the complexity for predictability, in current CPS, the plants are difficult to model precisely because they are non-deterministic, interactive and often scale to thousands of controllers. We outline research approaches to address these structural concerns in the design of future Cyber-Physical Systems through closed loop modeling, architectures, algorithms and platforms. The eventual goal of efforts such as this is to develop CPS to transform how we interact with and manipulate the physical world, just as the Internet transformed how we interact with information systems.

A key aspect of this cross-cutting work is that each challenge bridges two or more well-established scientific fields such as scheduling theory, control systems, formal methods, statistical machine learning, and experimentation. We illustrate this through five domain-specific problems spanning the safety of closed-loop medical devices, control over wireless, data-driven control of energy systems in volatile price markets, safe decision making in autonomous systems and co-design of computation and control for future automotive systems. We address the foundations of CPS across four themes: Modeling, Architectures, Algorithms and Platforms.
\begin{itemize}
\item \textbf{CPS Modeling:} From verified models into verified code for life-critical systems. We focus on the formal modeling, synthesis and certification of high-confidence medical device software and systems. We describe efforts on both implantable medical devices and physiological control systems to ensure that both the functional and formal aspects are verified, validated and tested within the closed-loop context of their physiological systems. 
\item \textbf{CPS Architectures:} Distributed Control over Wireless Networks. We describe radical architectural approaches for completely in-network computation for robust, optimal and secure control over unreliable infrastructure.
\item \textbf{CPS Algorithms:} Data-driven Controller Synthesis. In highly volatile electricity pricing markets, we required buildings and built environments to rapidly respond to peak pricing spikes. We describe a new data-driven approach for synthesis of control strategies to achieve real-time demand response while ensuring custom climate conditions are maintained.
\item \textbf{CPS Platforms and Test-beds:} To certify autonomous vehicles are safe we describe the experimental challenges with verifying decision controllers and executing them across a range of driving scenarios. As the perception and computation workload increase in such systems, we describe new approaches for the co-design of anytime computation with robust control. This allows the system to trade-off accuracy for faster responses and lower power requirements while ensuring the stability and tracking performance of the vehicle controls. 
\end{itemize}