

\documentclass[conference]{IEEEtran}



\usepackage[normalem]{ulem}
\usepackage{todonotes}

\newcommand{\mynote}[2]{\todo[inline]{#1 : #2}}
\newcommand{\quotes}[1]{``#1''}
\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage[per-mode=symbol]{siunitx} 
\usepackage{truonglatexdefs}
\usepackage{subfigure}


\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Five Challenge Problems in Cyber-Physical Systems}


% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Rahul Mangharam, Houssam Abbas, Madhur Behl, Kuk Jang, Zhihao Jiang, Matthew O'Kelly and Yash Vardhan Pant}
\IEEEauthorblockA{
%Department of Electrical \& Systems Engineering and Department of Computer and Information Science\\
School of Engineering and Applied Sciences\\
University of Pennsylvania\\
Philadelphia, Pennsylvania. USA 19104\\
Email: \{rahulm, habbas, mbehl, jangkj, zhihaoj, mokelly, yashpant\}@seas.penn.edu}}




% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}




% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The tight coupling of computation, communication and control with physical systems such as actuation of closed-loop medical devices within the human body, peak power minimization by coordination of controllers across large industrial plants, and fast life-critical decision making by autonomous vehicles, present a set of fundamental and unique challenges. Each of these require new approaches at the intersection of multiple scientific, human and systems disciplines. We discuss five such challenges which require creative insights and application of model-based design, control systems, scheduling theory, formal methods, statistical machine learning and domain-specific experimentation. We ask the following questions: 
(1) An autonomous medical device is implanted to control your heart over a period of 5-7 years. How do you guarantee the software in the device provides safe and effective treatment under all physiological conditions?
(2) Electricity prices in the US have summer peaks that are over 32x their average prices and winter peaks that are 86x. How can buildings respond to massive swings in energy prices at fast time scales?
(3) While wireless has been successfully used for open-loop monitoring and tracking, how can we operate closed-loop control systems over a network of wireless controllers. Furthermore, how can we ensure robust, optimal and secure control in the presence of node/link failures and topology changes?
(4) While autonomous vehicles have driven over a million miles, the most basic maneuvers, such as a lane change, are yet to be certified to be safe. How do we verify the safety of the decision controller in an autonomous system under all driving scenarios - in other words how can we provide a driver's license to a self-driving vehicle?
(5) In autonomous vehicles, when the computational resources of the hardware platform become overloaded, the estimation delay can compromise control performance and even stability. How can we co-design adaptive perception algorithms to operate with a fraction of the computing resources while ensuring the control stability and performance?

\end{abstract}

% no keywords




% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle


\input{intro}
\input{medical}
\input{dataCPES}
\input{wcn}
\input{automotive2}
\input{Anytime}

%\section{Conclusion}
%The conclusion goes here.




% conference papers do not normally have an appendix


% use section* for acknowledgment
%%\section*{Acknowledgment}


%%The authors would like to thank...





% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}

%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, %3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

%\end{thebibliography}

% Add you bibliographic information here...
\bibliographystyle{unsrt}
\bibliography{bibliography,bibliography2,IEEEabrv,mok,AnytimeBib,dataCPESrefs,WCNbibliography}




% that's all folks
\end{document}


